\documentclass[a4paper]{arthur-letter}

\title{Local Kailua-Kona security firms (Securitas, Viking, Aloha) succumb to Fascism. Ex US Navy SEAL Matthew Woods F.K.A. Burns detects a Hitler presence in the local police (i.e. Gestapo). US President Trump warns of the Lügenpresse. Fair and Balanced indeed.}

\author{Matthew Woods, F.K.A. Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods F.K.A. Burns}            % Your full name
\linkedin{matthew-burns-1581718}       % Your linkedin
\mail{mattwoods243@outlook.com}       % Your email
\numberphone{+1 808 445 9723}                % Your phone number
\lettitle{Local police and strip mall security firms team up to take on disabled Ex Navy SEAL Matthew Woods} % Title of your letter
\site{mattwoods5326.wixsite.com/xignalxincformerlyxi}                       % Your site
\github{XmattwoodsX}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

            \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. This is across five counties: San Diego, Orange, Santa Clara, Oahu and Hawaii. I think they may have ties to THE Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler and Eichmann of WWII. They lied to me about this since I was born. Target Corporation, local strip malls and police succumb to fascism and try to suppress me in all ways.}
            
            URGENT UPDATE RE Strip Malls
            
            \opening{Dear New York Times,}
            
            From my last letter, "Target Corporation Hitler Salute" \cite{targetcorporationhitlersalute}:
            
            "Furthermore, I have five other strip malls in Kailu-Kona which are exhibiting similar behavior. I'm going to sue them all as well, apparently for smaller amounts (e.g. 100's of thousands of dollars). I guess that is my job now as President/CEO."
            
            Just now \today, 
            Add two more fascist strip malls collaborating with local police in Kailua-Kona. This time, the officer hit me and stole my wine. This kind of bullying is common, but I'm not OK with the officers laying hands on me and throwing out my property. This reminds me of the Target Corporation incidents, complete with Nazi salutes and smashing my mobile device. Perhaps seven cops showed up. I sent video to NYT, et. al.
            \cite{alphabetinc} \cite{bigbangtheoryhouse5058pendleton}. 
            The police seem to be running these firms to the effect of suppresing me in all ways. Combine this with a Federal level hacking schema and I have a right to protest. Why am I unable to access my bank account? What is so hard about this? I think when Biden and Harris get into office, they will be able to see how much hacking has been done to me from the executive branch level. They are pieces of shit, and the cops apparently have something to say to me: "Hail Hydra!". 
            
            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods (F.K.A. Burns)}

    \end{letter}
\begin{thebibliography}{}

\bibitem{alphabetinc}
https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:8016c2b0-e71f-4c2c-995d-b67174459387

\bibitem{targetcorporationhitlersalute}
https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:f7522e8c-d944-449d-8fbd-f68dd59e60cb

\bibitem{bigbangtheoryhouse5058pendleton}
http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum= DV041758\&casesite=SD\&applcode=D

\end{thebibliography}
\end{document}